### 2020-03-24 korea.tex
ok done

Our study is not without limitations.
In particular, we did not account for differences in the delay distributions or changes in the number of tests among cities.
The intensity of intervention is likely to vary across regions given that majority of COVID-19 cases in South Korea were reported from Daegu.
We did not have sufficient data to account for these factors and therefore applied identical methods for adjusting the time series and estimating $\mathcal R_t$ across 4 regions.
Nonetheless, the robustness of our findings is supported by the sensitivity analyses (Supplementary Materials).
We also did not distinguish local and imported cases, which may overestimate $\mathcal R_t$ \citep{thompson2019improved}. \swp{The analysis of the Seoul outbreak which accounts for imported cases is presented in Supplementary Materials?}

>>>>

Our study is not without limitations.
In particular, we did not account for differences in the delay distributions or changes in the number of tests among cities.
The intensity of intervention is likely to vary across regions given that majority of COVID-19 cases in South Korea were reported from Daegu.
We did not have sufficient data to account for these factors and therefore applied identical methods for adjusting the time series and estimating $\mathcal R_t$ across 4 regions.
Nonetheless, the robustness of our findings is supported by the sensitivity analyses (Supplementary Materials).
We also did not distinguish local and imported cases, which may overestimate $\mathcal R_t$ \citep{thompson2019improved}.
We performed a separate analysis of the epidemic in Seoul that accounts for imported cases using line list provided by the Seoul Metropolitan Government; our qualitative conclusions remained robust (Supplementary Materials).

### 2020-03-24 supp.tex
ok done

For each combination of date of infection and a posterior sample of the forward delay distribution, we drew 1000 samples of incubation periods and onset-to-confirmation delays and calculated the median probability that an individual infected on a given day will be confirmed before March 16, 2020.
Finally, we divided the daily number of infected cases by the median probability that an infected case on a given day will be confirmed before Marh 16, 2020.

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_report_delay.pdf}
\caption{
\textbf{Changes in the number of tests and delay distributions over time.}
}
Vertical lines indicate the date on which testing criteria expanded.
Boxplots (C--D) represent the observed delays.
Black lines and gray ribbons represent the median estimates of the mean delays and their associated 95\% credible intervals.
\end{figure}

@@

>>>>

For each combination of date of infection and a posterior sample of the forward delay distribution, we drew 1000 samples of incubation periods and onset-to-confirmation delays and calculated the median probability that an individual infected on a given day will be confirmed before March 16, 2020.
Finally, we divided the daily number of infected cases by the median probability that an infected case on a given day will be confirmed before March 16, 2020.

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_report_delay.pdf}
\caption{
\textbf{Changes in the number of tests and delay distributions over time.}
}
Vertical lines indicate the date on which testing criteria expanded.
Box plots (C--D) represent the observed delays.
Black lines and gray ribbons represent the median estimates of the mean delays and their associated 95\% credible intervals.
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_R_t_seoul_linelist.pdf}
\caption{
\textbf{Comparison of effective reproduction number in Seoul using the number of reported cases by the KCDC and the line list provided by the Seoul Metropolitan Government.}
Using line list, we reconstructed incidence for local $I_t^{\textrm{local}}$ and imported $I_t^{\textrm{imported}}$ cases separately based on the method described in the main text. Then, we estimated the time-dependent reproduction number via $\mathcal R_t = I_t^{\textrm{local}}/\sum_{k=1}^{14} I_{t-k} w_k$, where $I_t=I_t^{\textrm{local}}+I_t^{\textrm{imported}}$. We did not account for changes in testing criteria in this analysis.
}
\end{figure}
